\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2020-04-01 gwnnDraft02.tex
rewording appendix

\begin{equation}\label{eqn::SWMHD}
\begin{split}
h^2\Omega_{v}^* = 1.6 \times 10^{-1} \, v  \, \bigg( \frac{\kappa_{v}\;  \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^1  S_{v}(f),
\\
h^2\Omega_{turb}^* = 2.01\times 10^{1} \, v \, \bigg( \frac{\kappa_{turb} \; \alpha}{1 + \alpha} \bigg)^{3/2} \bigg( \frac{H}{\beta} \bigg)^1  S_{turb}(f).
\end{split}
\end{equation}
Unlike the runaway case, we do not assume $v = 1$ due to the bubbles reaching a terminal velocity. The MHD efficiency factor is a fraction of the sound waves, $\kappa_{turb} = \epsilon\kappa_{v}$. Current simulations have motivated a range of $\epsilon \sim 0.05 - 0.10$  \citep{Caprini:2015zlo}, where we take the optimistic case of $\epsilon = 0.10$. Both contributions have unique spectral shapes, given to be \citep{Breitbach:2018ddu},

In the sound wave case, these parametizations are extracted from simulations with $\beta/H < 100$ corresponding to a long lasting sound wave component. For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time. When casting the model expectations for $\beta/H = 10^4$ we enter a regime at which ~(\ref{eqn::SNR}) may be overestimated the sound wave contribution. Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}. Although Independent of overestimating or signal, this paper focuses on the unique spectral shapes that are formed in these extraneous models. Therefore we project our results for high $\beta/H$ in Fig.~\ref{fig:Haasw}  to motivate the spectral profiles and not detectability.
%
\begin{equation}
\begin{split}
S_{v}(f) = (f/f_{p,v})^3\bigg(\frac{7}{4+3(f/f_{p,v})^2}\bigg)^{7/2},
\\
S_{turb}(f) = \frac{(f/f_{p,turb})^{3}}{(1 + f/f_{p,turb})^{11/3} (1 + 8\pi(f/H))}.
\end{split}
\end{equation}
The MHD energy density has a spectral shape dependent on the Hubble rate at the time of nucleation, $H$.  Similar to the scalar spectral shape in Eq.~(\ref{eqn::spectralshape}), the frequencies are scaled by their respective temperature dependent peak frequency,

\begin{equation}
\begin{split}
f_{p,v} = 1.9 \times 10^{-5} \, \textrm{Hz}\, \frac{1}{v} \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
\\
f_{p,turb} =  2.7 \times 10^{-5} \, \textrm{Hz}\, \frac{1}{v} \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
\end{split}
\end{equation}

We evolve the frequencies and energy densities with the same redshift factors, Eq.~(\ref{eqn::redshifting}) from Sec~\ref{sec:gw}. Fig.~\ref{fig:Haasw} shows the sum of the GW energy density for the scenarios in Table~\ref{tab:cases}, but instead for the non-runaway case, with a terminal velocity of $v = 0.95$. For this case we see that the spectra tend to be shifted to lower frequencies and are more likely to fall in the gap between the interferometers and the pulsar based detectors. On the other hand, larger values of $\beta/H$ increase the typical frequency, so this case becomes more sensitive in some scenarios to values of $\beta/H$ on the larger end of the considered range.

>>>>

\begin{equation}\label{eqn::SWMHD}
\begin{split}
h^2\Omega_{v}^* = 1.6 \times 10^{-1} \, v  \, \bigg( \frac{\kappa_{v}\;  \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^1  S_{v}(f),
\\
h^2\Omega_{turb}^* = 2.01\times 10^{1} \, v \, \bigg( \frac{\kappa_{turb} \; \alpha}{1 + \alpha} \bigg)^{3/2} \bigg( \frac{H}{\beta} \bigg)^1  S_{turb}(f).
\end{split}
\end{equation}
Unlike the runaway case, we do not assume $v = 1$ due to the bubbles reaching a terminal velocity. The MHD efficiency factor is a fraction of the sound waves, $\kappa_{turb} = \epsilon\kappa_{v}$. Current simulations have motivated a range of $\epsilon \sim 0.05 - 0.10$  \citep{Caprini:2015zlo}, where we take the optimistic case of $\epsilon = 0.10$. Both contributions have unique spectral shapes, given to be \citep{Breitbach:2018ddu}, 
%
\begin{equation}
\begin{split}
S_{v}(f) = (f/f_{p,v})^3\bigg(\frac{7}{4+3(f/f_{p,v})^2}\bigg)^{7/2},
\\
S_{turb}(f) = \frac{(f/f_{p,turb})^{3}}{(1 + f/f_{p,turb})^{11/3} (1 + 8\pi(f/H))}.
\end{split}
\end{equation}
The MHD energy density has a spectral shape dependent on the Hubble rate at the time of nucleation, $H$.  Similar to the scalar spectral shape in Eq.~(\ref{eqn::spectralshape}), the frequencies are scaled by their respective temperature dependent peak frequency,

\begin{equation}
\begin{split}
f_{p,v} = 1.9 \times 10^{-5} \, \textrm{Hz}\, \frac{1}{v} \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
\\
f_{p,turb} =  2.7 \times 10^{-5} \, \textrm{Hz}\, \frac{1}{v} \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}}.
\end{split}
\end{equation}
%
We evolve the frequencies and energy densities with the same redshift factors, Eq.~(\ref{eqn::redshifting}) from Sec~\ref{sec:gw}. Fig.~\ref{fig:Haasw} shows the sum of the GW energy density for the scenarios in Table~\ref{tab:cases}, but instead for the non-runaway case, with a terminal velocity of $v = 0.95$. For this case we see that the spectra tend to be shifted to lower frequencies and are more likely to fall in the gap between the interferometers and the pulsar based detectors. On the other hand, larger values of $\beta/H$ increase the typical frequency, so this case becomes more sensitive in some scenarios to values of $\beta/H$ on the larger end of the considered range.

In the sound wave case, these parametizations are extracted from simulations with $\beta/H < 100$ corresponding to a long lasting sound wave component. For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time. When estimating the model expectations for $\beta/H = 10^4$, we enter a regime at which Eq.~(\ref{eqn::SNR}) \draftnote{Is this the right equation reference?} may be overestimating the sound wave contribution. Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}. This effect, however, only affects the amplitude of the signal, and our work focuses on the unique spectral shapes that are formed in these models. Therefore we project our results for high $\beta/H$ in Fig.~\ref{fig:Haasw} to motivate the novel spectral profiles.
